---
title: "RWorksheet_Ceniza#2"
author: "Zydrick Ceniza"
date: "2023-10-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RWorksheet_Ceniza#2

##### Zydrick Ceniza BSIT-2B

### 1. Create a vector using : operator

a.  Sequence from -5 to 5. Write the R code and its output. Describe its output.

```{r}
num1<-seq(-5,5,by=1)
num1
```

the output sequence of is simply moving by 1 from -5 to the positive 5

b.  x \<- 1:7. What will be the value of x?

```{r}
x<-1:7
x
```

### 2. Create a vector using seq() function

a.  seq(1, 3, by=0.2) \# specify step size Write the R script and its output. Describe the output.

```{r}
num2<-seq(1, 3, by=0.2)
num2
```

the output sequence is simply moving by 0.2 from 1 to 3

### 3. A factory has a census of its workers. There are 50 workers in total. The following list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.

```{r}
workers_age<-c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)
workers_age
```

a.  Access 3rd element, what is the value?

```{r}
workers_age[3]
```

b.  Access 2nd and 4th element, what are the values?

```{r}
workers_age[c(2,4)]
```

c.  Access all but the 4th and 12th element is not included. Write the R script and its output

```{r}
workers_age[c(-4,-12)]
```

### 4. Create a vector x \<- c("first"=3, "second"=0, "third"=9). Then named the vector, names(x).

```{r}
x <- c("first"=3, "second"=0, "third"=9)
```

a.  Print the results. Then access x[c("first", "third")].

```{r}
x <- c("first"=3, "second"=0, "third"=9)
x[c("first", "third")]
```

Describe the output. The output only call the first and third and print its output

### 5. Create a sequence x from -3:2.

```{r}
x<- -3:2
x
```

a.  Modify 2nd element and change it to 0;

```{r}
x[2] <- 0
x
```

Describe the output. The output sequence x created have been changed the 2nd element to 0

### 6. \*The following data shows the diesel fuel purchased by Mr. Cruz.

a.  Create a data frame for month, price per liter (php)and purchase-quantity (liter). Write the R scripts and its output.

```{r}
num6<-data.frame(
Month=c("Jan", "Feb", "March","April","May","June"),
Liter<-c(52.50,57.25,60.00,65.00,74.25,54.00),
Purchase <-c(25,30,40,50,10,45)
)
colnames(num6) <- c("Month", "Price Per Liter(Php)", "Purchase-quantity(Liters)")
t(num6)
```

b.  What is the average fuel expenditure of Mr. Cruz from Jan to June? Note: Use 'weighted.mean(liter, purchase)'. Write the R scripts and its output

```{r}
weighted.mean(Liter,Purchase)
```

### 7. R has actually lots of built-in datasets. For example, the rivers data "gives the lengths (in miles) of 141"major" rivers in North America, as compiled by the US Geological Survey".

a.  Type "rivers" in your R console. Create a vector data with 7 elements, containing the number of elements (length) in rivers, their sum (sum), mean (mean), median(median), variance(var), standard deviation(sd), minimum (min) and maximum (max). data \<- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers))

```{r}
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers),sd(rivers), min(rivers), max(rivers))
data
```

b.  What are the results?

```{r echo=FALSE}
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers),sd(rivers), min(rivers), max(rivers))
#[1]    141.0000  83357.0000    591.1844    425.0000 243908.4086    493.8708    135.0000   3710.0000
```

### 8. The table below gives the 25 most powerful celebrities and their annual pay as ranked by the editions of Forbes magazine and as listed on the Forbes.com website.

a.  Create vectors according to the above table. Write the R scripts and its output.

```{r}
num8 <- data.frame(
Power<-c(1:25),
Celebrity<-c("Tom Cruise","Rolling Stones","Oprah Winfrey","U2","Tiger Woods","Steven Spielberg","Howard Stern","50 Cent","Cast of the Sopranos","Dan Brown","Bruce Springteen","Donald Trump","Muhammad Ali","Paul McCartney","George Lucas","Elton John","David Letterman","Phil Mickelson","J.K. Rowling","Bradd Pitt","Peter Jackson","Dr. Phil McGrew","Jay Lenon","Celine Dion","Kobe Bryant"),
  Pay<- c(67,90,225,110,90,332,302,41,52,88,55,44,55,40,233,34,40,47,75,25,39,45,32,40,31)
)
colnames(num8) <- c("Power Ranking", "Celebrity Name", "Pay")
num8
```

b.  Modify the power ranking and pay of J.K. Rowling. Change power ranking to 15 and pay to 90.\
    Write the R scripts and its output.

```{r}
num8 <- num8[c(1:14, 19, 15, 16:18, 20:25), ]
num8$Pay[15]<-90
num8$`Power Ranking`<-c(1:25)
num8
```

c.  Create an excel file from the table above and save it as csv file(PowerRanking). Import the csv file into the RStudio. What is the R script?

```{r}
library(readr)
PowerRanking <- read_csv("PowerRanking.csv")
View(PowerRanking)
```

d.  Access the rows 10 to 20 and save it as Ranks.RData. Write the R script and its output.

```{r}
PowerRanking[10:20,]
```

e.  Describe its output. The output is using a `[]` in the obect in order to specify the type of array you want to get like my answer 'PowerRanking[10:20,]' in order to get the 10 to 20 solution and the comma is simply seperating the rows and columns.

### 9. Download the Hotels-Vienna <https://tinyurl.com/Hotels-Vienna>

a.  Import the excel file into your RStudio. What is the R script?

```{r}
library(readr)
hotels_vienna_xlsx_hotels_vienna <- read_csv("hotels-vienna.xlsx - hotels-vienna.csv")
View(hotels_vienna_xlsx_hotels_vienna)
```

b.  How many dimensions does the dataset have?

```{r}
dim(hotels_vienna_xlsx_hotels_vienna)
```

c.  Select columns country, neighbourhood, price, stars, accomodation_type, and ratings. Write the R script.

```{r}
View(hotels_vienna_xlsx_hotels_vienna[c(1,6,7,9,22,24)])
num9c<-print.data.frame(hotels_vienna_xlsx_hotels_vienna[c(1,6,7,9,22,24)])
num9c
```

d.  Save the data as \*\*new.RData to your RStudio. Write the R script.

```{r}
write.csv(num9c, file = "new.RData")
```

e.  Display the first six rows and last six rows of the new.RData. What is the R script?

```{r}
library(readr)
new_RData <- read_csv("new.RData.csv")
View(new_RData)
new_RData[1:6,]
```

### 10. Create a list of ten (10) vegetables you ate during your lifetime. If none, just list down.

a.  Write the R scripts and its output.

```{r}
vegetable<-list("cabbage","tomato","eggplant","onions","potato","carrot","cucumber","radish","broccoli","garlic")
vegetable
```

b.  Add 2 additional vegetables after the last vegetables in the list. What is the R script and its output?

```{r}
vegetable_new1<-append(vegetable,c("spinach","olive"), after = 10)
vegetable_new1
```

c.  Add 4 additional vegetables after index 5. How many datapoints does your vegetable list have? What is the R script and its output?

```{r}
vegetable_new2<-append(vegetable_new1,c("pea","cauliflower","beans","mushroom"), after = 5)
vegetable_new2
```

d.  Remove the vegetables in index 5, 10, and 15. How many vegetables were left? Write the codes and its output.

```{r}
vegetable_new2[c(-5,-10,-15)]
```
