---
title: "RWorksheet_Ceniza#6"
author: "Zydrick Ceniza"
date: "2023-12-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Worksheet-6 in R (Individual Activity)
## RWorksheet_Ceniza#6

## Basic Statistics
### 1. Create a data frame for the table below. Show your solution.

#### a. Compute the descriptive statistics using different packages (Hmisc and pastecs).
Write the codes and its result.
```{r}

num1 <- data.frame(
  ID = c(1, 2, 3, 4, 5,6,7,8,9,10),
  Age = c(55,54,47,57,51,61,57,54,63,58),
  Salary = c(61,60,56,63,56,63,59,56,62,61)
)


num1


  install.packages("Hmisc")

  install.packages("pastecs")

library(Hmisc)
library(pastecs)


summary_hmisc <- Hmisc::describe(num1)
summary_hmisc


summary_pastecs <- pastecs::stat.desc(num1)
summary_pastecs


```

### 2. The Department of Agriculture was studying the effects of several levels of a fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.
```{r}
data <- c(10, 10, 10, 20, 20, 50, 10, 20, 10, 50, 20, 50, 20, 10)

ordered_factor <- factor(data, levels = c(10, 20, 50), ordered = TRUE)
summary(ordered_factor)
ordered_factor


```


## 3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense
### a. What is the best way to represent this in R?
```{r}

exercise_levels <- c("l", "n", "n", "i", "l", "l", "n", "n", "i", "l")

exercise_factor <- factor(exercise_levels, levels = c("n", "l", "i"), ordered = TRUE)
summary(exercise_factor)

exercise_factor


```


## 4. Sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as:
## state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld","vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa","vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld","vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa","vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")

set.seed(123)

sample_tax_accountants <- sample(state, 30, replace = TRUE)

print(sample_tax_accountants)
```









