---
title: "RWorksheet_Ceniza#6"
author: "Zydrick Ceniza"
date: "2023-12-06"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Worksheet-6 in R (Individual Activity)
## RWorksheet_Ceniza#6

## Basic Statistics
### 1. Create a data frame for the table below. Show your solution.

#### a. Compute the descriptive statistics using different packages (Hmisc and pastecs).
Write the codes and its result.
```{r}

num1 <- data.frame(
  ID = c(1, 2, 3, 4, 5,6,7,8,9,10),
  Age = c(55,54,47,57,51,61,57,54,63,58),
  Salary = c(61,60,56,63,56,63,59,56,62,61)
)


num1


  install.packages("Hmisc")

  install.packages("pastecs")

library(Hmisc)
library(pastecs)


summary_hmisc <- Hmisc::describe(num1)
summary_hmisc


summary_pastecs <- pastecs::stat.desc(num1)
summary_pastecs


```

### 2. The Department of Agriculture was studying the effects of several levels of a fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.
```{r}
data <- c(10, 10, 10, 20, 20, 50, 10, 20, 10, 50, 20, 50, 20, 10)

ordered_factor <- factor(data, levels = c(10, 20, 50), ordered = TRUE)
summary(ordered_factor)
ordered_factor


```


## 3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense
### a. What is the best way to represent this in R?
```{r}

exercise_levels <- c("l", "n", "n", "i", "l", "l", "n", "n", "i", "l")

exercise_factor <- factor(exercise_levels, levels = c("n", "l", "i"), ordered = TRUE)
summary(exercise_factor)

exercise_factor


```



## 4. Sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as:
## state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld","vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa","vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld","vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa","vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")

statef <- factor(state)

statef

```

### 5. From #4 - continuation: • Suppose we have the incomes of the same tax accountants in another vector (in suitably large units of money)
## incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48, 65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
## a. Calculate the sample mean income for each state we can now use the special function tapply(): Example: giving a means vector with the components labelled by the levelsincmeans <- tapply(incomes, statef, mean)
```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48, 65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)

levelsincmeans <- tapply(incomes, statef, mean)

levelsincmeans

```

## b. Copy the results and interpret.
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld","vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa","vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48, 65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)

levelsincmeans <- tapply(incomes, statef, mean)

levelsincmeans

summary(levelsincmeans)
```
`The "tas" has the highest mean of 60.50 and "act" that has the shortest mean of 44.50`

## 6. Calculate the standard errors of the state income means (refer again to number 3) stdError <- function(x) sqrt(var(x)/length(x)) Note: After this assignment, the standard errors are calculated by: incster <- tapply(incomes, statef, stdError)

### a. What is the standard error? Write the codes.
```{r}

stdError <- function(x) sqrt(var(x) / length(x))

incster <- tapply(incomes, statef, stdError)

incster


```
### b. Interpret the result.
`The functiion compute the desired computaions such as dividing var and length inside the sqr.`
`A larger standard error indicates greater variability in the income means for that state. Lower standard errors suggest more precision in estimating the true population mean for each state.`

## 7.Use the titanic dataset.

### a. subset the titatic dataset of those who survived and not survived. Show the codes and its result.
```{r}

titanic<-as.data.frame(Titanic)
titanic
survived <- subset(titanic, Survived == 'Yes')
survived
not_survived <- subset(titanic, Survived == 'No')
not_survived


```

## 8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically as Dr. Wolberg reports his clinical cases. The database therefore reflects this

### a. describe what is the dataset all about.
`The data set is all about is all about the breast cancer diagnosis`
```{r}
library(readr)
breastcancer_wisconsin <- read_csv("breastcancer_wisconsin.csv")
breastcancer_wisconsin
str(breastcancer_wisconsin)
```
d. Compute the descriptive statistics using different packages. Find the values of:
d.1 Standard error of the mean for clump thickness.
```{r}
stdError <- function(x) sqrt(var(x) / length(x))
er_clump_thickness<-stdError(breastcancer_wisconsin$clump_thickness)
er_clump_thickness
```
d.2 Coefficient of variability for Marginal Adhesion.
```{r}
coe_marginal_adhesion <- sd(breastcancer_wisconsin$marginal_adhesion) / mean(breastcancer_wisconsin$marginal_adhesion)
coe_marginal_adhesion

```

d.3 Number of null values of Bare Nuclei.
```{r}
null<-sum(is.na(breastcancer_wisconsin$bare_nucleoli))
null

```
d.4 Mean and standard deviation for Bland Chromatin
```{r}
mean_bland_chromatin <- mean(breastcancer_wisconsin$bland_chromatin)
sd_bland_chromatin <- sd(breastcancer_wisconsin$bland_chromatin)
print(paste("Mean:", mean_bland_chromatin, " SD:", sd_bland_chromatin))

```

d.5 Confidence interval of the mean for Uniformity of Cell Shape
```{r}
library(stats)
ci_uniformity_cell_shape <- t.test(breastcancer_wisconsin$shape_uniformity)$conf.int
print(ci_uniformity_cell_shape)
```

### d. How many attributes?
```{r}
ncol(breastcancer_wisconsin)
```

### e. Find the percentage of respondents who are malignant. Interpret the results.
```{r}
malignant_percentage <- (sum(breastcancer_wisconsin$class == 4) / nrow(breastcancer_wisconsin)) * 100

# Display the result
malignant_percentage

```

## 9. Export the data abalone to the Microsoft excel file. Copy the codes.

install.packages("AppliedPredictiveModeling")
library("AppliedPredictiveModeling")
View(abalone)
head(abalone)
summary(abalone)

save(abalone, file="abalone.csv")









