---
title: "RWorksheet_Ceniza#6"
author: "Zydrick Ceniza"
date: "2023-12-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Worksheet-6 in R (Individual Activity)
## RWorksheet_Ceniza#6

## Basic Statistics
### 1. Create a data frame for the table below. Show your solution.

#### a. Compute the descriptive statistics using different packages (Hmisc and pastecs).
Write the codes and its result.
```{r}
# Assuming you have a dataset like this
num1 <- data.frame(
  ID = c(1, 2, 3, 4, 5,6,7,8,9,10),
  Age = c(55,54,47,57,51,61,57,54,63,58),
  Salary = c(61,60,56,63,56,63,59,56,62,61)
)

# Print the created data frame
num1

# Install and load necessary packages
  install.packages("Hmisc")

  install.packages("pastecs")

library(Hmisc)
library(pastecs)

# Descriptive statistics using Hmisc
summary_hmisc <- Hmisc::describe(data)
print(summary_hmisc)

# Descriptive statistics using pastecs
summary_pastecs <- pastecs::stat.desc(data)
print(summary_pastecs)


```

### 2. The Department of Agriculture was studying the effects of several levels of a fertilizer
on the growth of a plant. For some analyses, it might be useful to convert the fertilizer
levels to an ordered factor.