---
title: "RWorksheet_Ceniza#4a"
author: "Zydrick Ceniza"
date: "2023-10-25"
output:
  pdf_document: default
  html_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Worksheet-4a in R

### Zydrick Ceniza BSIT-2B

## 1. The table below shows the data about shoe size and height. Create a data frame.

a.  Describe the data. The data imported choose the column shoes size
    and height

```{r}
library(readxl)
Shoes <- read_excel("Shoes.xlsx")
Shoes[,1:2]
str(Shoes)
```

b.  Create a subset by males and females with their corresponding shoe
    size and height. What its result? Show the R scripts.

```{r}
subsetMale <- subset(Shoes,Gender == "M")
subsetMale
subsetFemale <- subset(Shoes,Gender == "F")
subsetFemale
```

c.  Find the mean of shoe size and height of the respondents. Write the
    R scripts and its result.

```{r}
num1c<-factor
mean(Shoes$`Shoe size`)
mean(Shoes$Height)
```

d.  Is there a relationship between shoe size and height? Why?
Yes, there is a relationship between shoe size and height like the taller you are the bigger the shoes size.

##2. Construct character vector months to a factor with factor() and
assign the result to factor_months_vector. Print out
factor_months_vector and assert that R prints out the factor levels
below the actual values. Consider data consisting of the names of
months:
"March","April","January","November","January","September","October","September","November","August","January","November","November","February","May","August","July","December","August","August","September,"November","February",April")

```{r}
months_vector <- c("March", "April", "January", "November", "January","September", "October", "September", "November", "August","January", "November", "November", "February", "May", "August","July", "December", "August", "August", "September", "November", "February", "April")

factor_months_vector <- factor(months_vector)

factor_months_vector
```

##3. Then check the summary() of the months_vector and
factor_months_vector. \| Inter-pret the results of both vectors. Are
they both equally useful in this case?

```{r}
summary(months_vector)
summary(factor_months_vector)
#The result in summary of months_vector it just interpret the length, class, and mode of it and in the summary of factors_months_vectors it interpret how many number the months repeat itself in a vector.
```

The result in summary of months_vector it just interpret the length,
class, and mode of it and in the summary of factors_months_vectors it
interpret how many number the months repeat itself in a vector.

##4. Create a vector and factor for the table below.

```{r}
factor_data<-c("East","West","North","West","North","North","West","West")
new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
dir<-c("East","West","West","North","West","North","West","North")
dirsum<-factor(dir)
summary(dirsum)
num4<-data.frame(
  Direction=c("East","West","North"),
  Frequency=c(1,4,3)
)
num4

```

##5. Enter the data below in Excel with file name = import_march.csv

a\. Import the excel file into the Environment Pane using read.table()
function. Write the code.

```{r}
library(readr)
data <- read.table("import_march.csv", header = TRUE, sep = ",")
data
```

b.  View the dataset. Write the R scripts and its result.

```{r}
View(data)
```

#Using Conditional Statements (IF-ELSE)

##6. Full Search Exhaustive search is a methodology for finding an
answer by exploring all possible cases. When trying to find a desired
number in a set of given numbers, the method of finding the
corresponding number by checking all elements in the set one by one can
be called an exhaustive search. Implement an exhaustive search function
that meets the input/output conditions below.

a.  Create an R Program that allows the User to randomly select numbers
    from 1 to 50. Then display the chosen number. If the number is
    beyond the range of the selected choice, it will have to display a
    string "The number selected is beyond the range of 1 to 50". If
    number 20 is inputted by the User, it will have to display "TRUE",
    otherwise display the input number.

```{r}
num6a<-readline(prompt = "Enter a number 1 to 50")
if(num6a>=50){
  print("The number selected is beyond the range of 1 to 50")
} else if(num6a==20){
  print("TRUE")
} else{
  num6a
}
```

## 7. Change

At ISATU University's traditional cafeteria, snacks can only be
purchased with bills. A long-standing rule at the concession stand is
that snacks must be purchased with as few coins as possible. There are
three types of bills: 50 pesos, 100 pesos, 200 pesos, 500 pesos, 1000
pesos. a. Write a function that prints the minimum number of bills that
must be paid, given the price of the snack. Input: Price of snack (a
random number divisible by 50) Output: Minimum number of bills needed to
purchase a snack.

```{r}
bills <- c(1000, 500, 200, 100, 50)
price<-as.numeric(readline(prompt = "Enter a price"))
if(price< 50) {
  print("Price is too low. Cannot provide change.")
} else if (price == 50) {
  print("Minimum bills is")
  print(bills[5])
} else if (price < 150) {
  print("Minimum bills are")
  print(bills[c(5, 4)])
} else if (price < 450) {
  print("Minimum bills are")
  print(bills[c(5, 4, 3)])
} else if (price < 950) {
  print("Minimum bills are")
  print(bills[c(5, 4, 3, 2)])
} else if (price >= 1000) {
  print("Minimum bills are")
  print(bills)
}

```

## 8. The following is each student's math score for one semester. Based on this, answer the following questions.

a.  Create a dataframe from the above table. Write the R codes and its
    output.

```{r}
num8a<-data.frame(
  Name=c("Annie","Thea","Steve","Hanna"),
  Grade1=c(85,65,75,95),
  Grade2=c(65,75,55,75),
  Grade3=c(85,90,80,100),
  Grade4=c(100,90,85,90)
)
num8a
```

b.  Without using the rowMean function, output the average score of
    students whose average math score over 90 points during the
    semester. write R code and its output. Example Output: Annie's
    average grade this semester is 88.75.

```{r}
Average <- (num8a$Grade1 + num8a$Grade2 + num8a$Grade3 + num8a$Grade4) / 4
num8a$Average<-c(Average)
high_avg_students <- num8a[num8a$Average > 90,]
i<-c(1:4)
if(num8a$Average[1]> 90){
  cat(num8a$Name[1], "'s average grade this semester is ", num8a$Average[1], ".\n")
} else if(num8a$Average[2]> 90){
  cat(num8a$Name[2], "'s average grade this semester is ", num8a$Average[2], ".\n")
} else if(num8a$Average[3]> 90){
  cat(num8a$Name[3], "'s average grade this semester is ", num8a$Average[3], ".\n")
} else if(num8a$Average[4]> 90){
  cat(num8a$Name[4], "'s average grade this semester is ", num8a$Average[4], ".\n")
}


```

c.  Without using the mean function, output as follows for the tests in
    which the average score was less than 80 out of 4 tests. Example
    output: The nth test was difficult.

```{r}
term<-c("1st","2nd","3rd","4th")
average1<-sum(num8a$Grade1)/4
average2<-sum(num8a$Grade2)/4
average3<-sum(num8a$Grade3)/4
average4<-sum(num8a$Grade4)/4
if(average1<80){
  cat("The",term[1],"testwas difficult.")
}else if(average2<80){
  cat("The",term[2],"testwas difficult.")
}else if(average3<80){
  cat("The",term[3],"testwas difficult.")
}else if(average4<80){
  cat("The",term[4],"testwas difficult.")
}
```

d.  Without using the max function, output as follows for students whose
    highest score for a semester exceeds 90 points. Example Output:
    Annie's highest grade this semester is 95.

```{r}
for(i in 1:4){
  if(num8a$Grade1[i]>90){
  cat(num8a$Name[i], "highest grade this semester is ", round(num8a$Grade1[i],2), ".\n")
  }}
for(i in 1:4){
  if(num8a$Grade2[i]>90){
  cat(num8a$Name[i], "highest grade this semester is ", round(num8a$Grade2[i],2), ".\n")
  }}
for(i in 1:4){
  if(num8a$Grade3[i]>90){
  cat(num8a$Name[i], "highest grade this semester is ", round(num8a$Grade3[i],2), ".\n")
  }}
for(i in 1:4){
  if(num8a$Grade4[i]>90){
  cat(num8a$Name[i], "highest grade this semester is ", round(num8a$Grade4[i],2), ".\n")
}}
```
