---
title: "RWorksheet_Ceniza#4b"
author: "Zydrick Ceniza"
date: "2023-11-07"
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RWorksheet_4b

### Zydrick Ceniza

## Using Loop Function

for() loop \### 1. Using the for loop, create an R script that will
display a 5x5 matrix as shown in

Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.
Hint Use abs() function to get the absolute value

```{r}
vectorA <- c(1, 2, 3, 4, 5)

matrixB <- matrix(0, nrow = 5, ncol = 5)

for (i in 1:5) {
  for (j in 1:5) {
    matrixB[i, j] <- abs(vectorA[i] - vectorA[j])
  }
}

matrixB

```

### 2. Print the string "\*" using for() function. The output should be the same as shown

in Figure

```{r}
num2 <- 5

for (i in 1:num2) {
  cat(paste(rep("*", i), collapse = ""), "\n")
}
```

### 3. Get an input from the user to print the Fibonacci sequence starting from the 1st input up to 500. Use repeat and break statements. Write the R Scripts and its output.

```{r}

b<- as.numeric(readline("Enter the number of terms you want in the Fibonacci sequence: "))

a <- 0
b<-1
cat("Fibonacci sequence:\n",a)
count <- 2 
repeat {
  next_term <- a + b
  

  if (next_term > 500) {
    break
  }
  

  cat(" ", next_term)
  a <- b
  b <- next_term
}

```

## Using Basic Graphics (plot(),barplot(),pie(),hist())

### 4. Import the dataset as shown in Figure 1 you have created previously.

a.  What is the R script for importing an excel or a csv file? Display
    the first 6 rows of the dataset? Show your codes and its result

```{r}
library(readxl)
Shoes <- read_excel("Shoes.xlsx")
Shoes
head(Shoes)
```

b.  Create a subset for gender(female and male). How many observations
    are there in Male? How about in Female? Write the R scripts and its
    output.

```{r}
subsetMale <- subset(Shoes,Gender == "M")
subsetMale
subsetFemale <- subset(Shoes,Gender == "F")
subsetFemale
```

`There are 14 observation in Male and 14 observation also in Female`

c.  Create a graph for the number of males and females for Household
    Data. Use plot(), chart type = barplot. Make sure to place title,
    legends, and colors. Write the R scripts and its result.

```{r}
library(ggplot2)
library(readr)
HouseholdData<-read.csv("HouseholdData.csv")

bm <- subset(HouseholdData, Sex == "Male")
bf <- subset(HouseholdData, Sex == "Female")
colors <- c("blue", "pink")

barplot(
  c(nrow(bm), nrow(bf)),
  names.arg = c("Male","Female"),
  col = colors,
  main = "Number of Males and Females",
  xlab = "Gender",
  ylab = "Number"
)

legend("topright", legend = c("Male","Female"), fill = colors, title = "Categories")
```

### 5. The monthly income of Dela Cruz family was spent on the following:

a.  Create a piechart that will include labels in percentage.Add some
    colors and title of the chart. Write the R scripts and show its
    output.

```{r}
data <- c(60, 10, 5, 25)
labels <- c("Food", "Electricity", "Savings", "Miscellaneous")

colors <- c("maroon", "pink", "skyblue", "purple")


pie(data, labels = labels, col = colors)

legend("bottomright", legend = labels, fill = colors, title = "Categories")

title("The monthly spent of Dela Cruz family")

```

### 6. Use the iris dataset.

```{r}
data(iris)
iris
```

a.  Check for the structure of the dataset using the str() function.
    Describe what you have seen in the output.

```{r}
str(iris)
```

`The str function tells the structure of the iris data set, that there are 150 objects in 5 variables`

b.  Create an R object that will contain the mean of the sepal.length,
    sepal.width,petal.length,and petal.width. What is the R script and
    its result?

```{r}
num6b<-mean(iris$Sepal.Length)
num6b
```

c.  Create a pie chart for the Species distribution. Add title, legends,
    and colors. Write the R script and its result.

```{r}
data(iris)

species_counts <- table(iris$Species)

colors <- c("setosa" = "red", "versicolor" = "green", "virginica" = "blue")

pie(species_counts, labels = species_counts, col = colors)

legend("topright", legend = names(species_counts), fill = colors, title = "Species")

title("Species Distribution in Iris Dataset")

```

d.  Subset the species into setosa, versicolor, and virginica. Write the
    R scripts and show the last six (6) rows of each species.

```{r}
data(iris)

dsetosa<- subset(iris,Species == 'setosa' )
tail(dsetosa)
dversicolor<-subset(iris,Species == 'versicolor' )
tail(dversicolor)
dvirginica<-subset(iris,Species == 'virginica' )
tail(dvirginica)



```

e.  Create a scatterplot of the sepal.length and sepal.width using the
    different species(setosa,versicolor,virginica). Add a title = "Iris
    Dataset", subtitle = "Sepal width and length, labels for the x and y
    axis, the pch symbol and colors should be based on the species.

```{r}
library(ggplot2)
scatterplot <- ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species, shape = Species)) +
  geom_point(size = 3) +
  labs(
    title = "Iris Dataset",
    subtitle = "Sepal width and length",
    x = "Sepal Length",
    y = "Sepal Width"
  ) +
  scale_shape_manual(values = c(16, 17, 18)) +
  scale_color_manual(values = c("setosa" = "red", "versicolor" = "green", "virginica" = "blue"))

scatterplot
```



f.  Interpret the result. 
'Setosa have the bigger sepal width and Virginica have the highest sepal length, while the versicolor is in equal in length and in width'

## Basic Cleaning and Transformation of Objects

7.  Import the alexa-file.xlsx. Check on the variations. Notice that
    there are extra whitespaces among black variants (Black Dot, Black
    Plus, Black Show, Black Spot). Also on the white variants (White
    Dot, White Plus, White Show, White Spot).

```{r}
library(readxl)
alexa_file <- read_excel("alexa_file.xlsx")

```

a.  Rename the white and black variants by using gsub() function.

```{r}
alexa_file$variation <- gsub("Black", "black",alexa_file$variation)
alexa_file$variation <- gsub("White", "white",alexa_file$variation)
alexa_file

```


Syntax:
RObject$columnName <- gsub("Old Name", "New Name", RObject$columnName)
Write the R scripts and show an example of the output by getting a snippet. To embed
an image into Rmd, use the function below:
knitr::include_graphics("file path")
# knitr::include_graphics("file path")
knitr::include_graphics("E:/RBasics/R_Directory/CS101(lectures_23)/BasicsOfR/RBasics/notes/images/m2.JPG")


b. Get the total number of each variations and save it into another object. Save the
object as variations.RData. Write the R scripts. What is its result?
Hint: Use the dplyr package. Make sure to install it before loading the package.
Syntax for dplyr
RObject %>%
count(RObject$columnName)
```{r}
install.packages("dplyr")
```

```{r}
library(readxl)
library(dplyr)
alexa_files <- read_excel("alexa_file.xlsx")
variation_counts <-alexa_files %>%
  count(variation)

save(variation_counts, file = "variations.RData")


variation_counts
```


Sample Output
c. From the variations.RData, create a barplot(). Complete the details of the chart
which include the title, color, labels of each bar.
```{r}
library(readr)
load("variations.RData")


```

d. Create a barplot() for the black and white variations. Plot it in 1 frame, side by
side. Complete the details of the chart.
Example:
```{r}
library(ggplot2)
b1<-subset(alexa_files,variation=="Black")
b2<-subset(alexa_files,variation=="Black Dot")
b3<-subset(alexa_files,variation=="Black Plus")
b4<-subset(alexa_files,variation=="Black Show")
b5<-subset(alexa_files,variation=="Black Spot")
colors<-c("black","maroon","green","blue","skyblue")
barplot(
  c(nrow(b1), nrow(b2), nrow(b3), nrow(b4), nrow(b5)),
  names.arg = c("Black","Black Dot", "Black Plus","Black Show","Black Spot"),
  col = colors,
  main = "Black Variants",
  xlab = "Total Numbers",
  ylab = "Variants"
)

legend("right", legend = c("Black","Black Dot", "Black Plus","Black Show","Black Spot"), fill = colors, title = "Categories")

```

```{r}
library(ggplot2)
b1<-subset(alexa_files,variation=="White")
b2<-subset(alexa_files,variation=="White Dot")
b3<-subset(alexa_files,variation=="White Plus")
b4<-subset(alexa_files,variation=="White Show")
b5<-subset(alexa_files,variation=="White Spot")
colors<-c("black","maroon","green","blue","skyblue")
barplot(
  c(nrow(b1), nrow(b2), nrow(b3), nrow(b4), nrow(b5)),
  names.arg = c("White","White Dot", "White Plus","White Show","White Spot"),
  col = colors,
  main = "White Variants",
  xlab = "Total Numbers",
  ylab = "Variants"
)

legend("right", legend = c("White","White Dot", "White Plus","White Show","White Spot"), fill = colors, title = "Categories")

```














