---
title: "RWorksheet_Ceniza#4c"
author: "Zydrick Ceniza"
date: "2023-11-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RWorksheet_Ceniza#4c

### 1. Use the dataset mpg

### a. Show your solutions on how to import a csv file into the environment.

```{r}
library(readr)
mpg <- read.csv("mpg.csv")
mpg
```

### b. Which variables from mpg dataset are categorical?

### c. Which are continuous variables?

## 2. Which manufacturer has the most models in this data set? Which model has the most variations?

Show your answer.`The manufacturer has the most model is the dodge and caravan 2wd has the most models in the manufacturer of dodge`

```{r}
num1a<-factor(mpg$manufacturer)
num1a1<-summary(num1a)
num1a1
max(num1a1)
md<-factor(mpg$model)
summary(md)
max(summary(md))
```

### a. Group the manufacturers and find the unique models. Show your codes and result
```{r}
num1a<-factor(mpg$manufacturer)
num1a1<-summary(num1a)
num1a1
```

### b. Graph the result by using plot() and ggplot(). Write the codes and its result.

```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point() + scale_color_manual(values = c("audi" = "red", "chvrolet" = "green", "dodge" = "blue","ford"="purple","honda"="violet","hyundai"="pink","jeep"="yellow","land rover"="orange","lincoln"="maroon","mercury"="skyblue","nissan"="grey","pontiac"="white","subaru"="black","toyota"="brown","volkswagen"="orangered"))

```

## 2. Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.

## a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
`The plot shows the model and manufacturer in a black and white color`
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
## b. For you, is it useful? If not, how could you modify the data to make it more informative?
`Yes,it is useful in order make a comparison to make decisions and soltuions.`

## 3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and its results.
```{r}

ggplot(mpg, aes(model, year)) + geom_point()
```

## 4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result.
```{r}

library(dplyr)
num4<-mpg %>% 
 group_by(model) %>% 
 summarise(count = n()) %>% 
 arrange(desc(count))

num4
```
### a. Plot using geom_bar() using the top 20 observations only. The graphs shoudl have a title, labels and colors. Show code and results.
```{r}
ob20<-num4[1:20,1:2]
ggplot(num4, aes(model, count)) + geom_point()
```
### b. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.
```{r}
ggplot(num4, aes(x = model, y = count)) +
 geom_bar(stat = "identity", fill = "skyblue") +
 coord_flip() +
 theme_minimal() +
 labs(title = "Number of Cars per Model",
      x = "Model",
      y = "Count") +
 scale_x_discrete(limits =num4$model)

```

