---
title: "RWorksheet_Ceniza#4c"
author: "Zydrick Ceniza"
date: "2023-11-21"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RWorksheet_Ceniza#4c

### 1. Use the dataset mpg

### a. Show your solutions on how to import a csv file into the environment.

```{r}
library(readr)
mpg <- read_csv("mpg.csv")
mpg
```

### b. Which variables from mpg dataset are categorical?

```{r}
categorical <- sapply(mpg, function(x) is.factor(x) || is.character(x))
cat("Categorical Variables:", names(mpg)[categorical])



```

### c. Which are continuous variables?

```{r}
continuous <- sapply(mpg, function(x) is.numeric(x) && !is.factor(x) && !is.character(x))
cat("Continuous Variables:", names(mpg)[continuous])

```

## 2. Which manufacturer has the most models in this data set? Which model has the most variations?

Show your answer.`The manufacturer has the most model is the dodge and caravan 2wd has the most models in the manufacturer of dodge`

```{r}

md<-factor(mpg$model)
summary(md)
cat("The most models is the caravan 2wd that has:",max(summary(md)))
num1a<-factor(mpg$manufacturer)
num1a1<-summary(num1a)
num1a1 
cat("The model that has the most variation is the dodge that have:",max(num1a1))
```

### a. Group the manufacturers and find the unique models. Show your codes and result

```{r}
num1a<-factor(mpg$manufacturer)
num1a1<-summary(num1a)
num1a1
```

### b. Graph the result by using plot() and ggplot(). Write the codes and its result.

```{r}
library(ggplot2)
ggplot(mpg, aes(x = model, y = manufacturer, color=class)) + geom_point()

```

## Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.

## a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?

`The plot shows the model and manufacturer in a black and white color`

```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

## b. For you, is it useful? If not, how could you modify the data to make it more informative?

`Yes,it is useful in order make a comparison to make decisions and soltuions.`

## 3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and its results.

```{r}
num3mpg<-mpg[1:20,]
ggplot(num3mpg, aes(x = model, y = year, color=model )) + geom_point(size=3)
```

## 4. Using the pipe (%\>%), group the model and get the number of cars per model. Show codes and its result.

```{r}

library(dplyr)
num4<-mpg %>% 
 group_by(model) %>% 
 summarise(count =n())


num4
```

### a. Plot using geom_bar() using the top 20 observations only. The graphs shoudl have a title, labels and colors. Show code and results.

```{r}
ob20<-num4[1:20,1:2]

ggplot(ob20, aes(x = model, y = count, fill = model)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Number of Cars per Model (Top 20)",
       x = "Model",
       y = "Number of Cars") +
  scale_fill_hue()

```

### b. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.

```{r}
library(ggplot2)

ggplot(ob20, aes(x = model, y = count, fill = model)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Number of Cars per Model (Top 20)",
       x = "Model",
       y = "Number of Cars") +
  scale_fill_hue()


```

## 5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic color = engine displacement. Title should be "Relationship between No. of Cylinders and Engine Displacement".

### a. How would you describe its relationship? Show the codes and its result.

```{r}
library(ggplot2)

ggplot(mpg, aes(x = cyl, y = displ, color = displ)) +
  geom_point() +
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders",
       y = "Engine Displacement",
       color = "Engine Displacement")
```

## 6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped it with a continuous variable you have identified in #1-c. What is its result? Why it produced such output?

```{r}
library(ggplot2)
ggplot(mpg, aes(x = displ, y = hwy, color = hwy)) +
  geom_point() +
  labs(title = "Relationship between Engine Displacement and Highway Miles per Hour",
       x = "Engine Displacement",
       y = "Highway Miles per Hour",
       color = "Highway Miles per Hour")

```

## 6. Import the traffic.csv onto your R environment.

```{r}
library(ggplot2)
traffic<-ggplot(num4, aes(x = model, y = count, fill = model)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Number of Cars per Model",
       x = "Model",
       y = "Number of Cars") +
  scale_fill_hue()+ guides(fill=FALSE)
traffic
save(traffic,file = "traffic.csv")
load(file="traffic.csv")
traffic

```

### a. How many numbers of observation does it have? What are the variables of the traffic dataset the Show your answer.

```{r}

cat("The number of observations are:\n")
nrow(traffic$data)
cat("The variables of traffic dataset are:\n" )
colnames(traffic$data)
```

### b. subset the traffic dataset into junctions. What is the R codes and its output?

```{r}

```

### c. Plot each junction in a using geom_line(). Show your solution and output.

```{r}

```

## 7. From alexa_file.xlsx, import it to your environment

```{r}
library(readxl)
alexa_file <- read_excel("alexa_file.xlsx")
```

### a. How many observations does alexa_file has? What about the number of columns? Show your solution and answer.

```{r}
cat("The number of observations in alexa_file are:\n ")
nrow(alexa_file)
cat("The number of columns in alexa_file are:\n ")
ncol(alexa_file)
```

### b. group the variations and get the total of each variations. Use dplyr package. Show solution and answer.

```{r}
library(dplyr)
num7<-alexa_file %>% 
 group_by(variation) %>% 
 summarise(count = n())
num7

```

### c. Plot the variations using the ggplot() function. What did you observe? Complete the details of the graph. Show solution and answer.

```{r}
library(ggplot2)
ggplot(num7, aes(x=variation,y=count,fill=variation))+geom_bar(stat="Identity")+coord_flip() +
  theme_minimal() +
  labs(title = "Number of Variations per count",
       x = "Variations",
       y = "count")


```

### d. Plot a geom_line() with the date and the number of verified reviews. Complete the details of the graphs. Show your answer and solution.

```{}
library(ggplot2)

ggplot(alexa_file, aes(x = verified_reviews, y = date)) +
  geom_line(color = "skyblue") +
  geom_point(color = "violet", size = 2) +
  labs(title = "Verified Reviews Over Time",
       x = "Number of Verified Reviews",
       y = "Date") +
  theme_minimal()

```

### e. Get the relationship of variations and ratings. Which variations got the most highest in rating? Plot a graph to show its relationship. Show your solution and answer

`The Highest rating is the Black Dot`

```{r}

ggplot(alexa_file, aes(x=variation ,y=rating,fill=variation))+
  geom_bar(stat="Identity")+
  coord_flip() +
  labs(title = "Number of Variations per count",
       x = "Variations",
       y = "count")

```
