---
title: "RWorksheet_Ceniza#4b"
author: "Zydrick Ceniza"
date: "2023-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RWorksheet_4b
### Zydrick Ceniza

## Using Loop Function
for() loop
### 1. Using the for loop, create an R script that will display a 5x5 matrix as shown in

Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.
Hint Use abs() function to get the absolute value

```{r}
vectorA <- c(1, 2, 3, 4, 5)

matrixB <- matrix(0, nrow = 5, ncol = 5)

for (i in 1:5) {
  for (j in 1:5) {
    matrixB[i, j] <- abs(vectorA[i] - vectorA[j])
  }
}

matrixB

```

### 2. Print the string "*" using for() function. The output should be the same as shown
in Figure
```{r}
num2 <- 5

for (i in 1:num2) {
  cat(paste(rep("*", i), collapse = ""), "\n")
}
```

### 3. Get an input from the user to print the Fibonacci sequence starting from the 1st input up to 500. Use repeat and break statements. Write the R Scripts and its output.
 
```{r}
 # Get input from the user
n <- as.numeric(readline("Enter the number of terms you want in the Fibonacci sequence: "))

# Initialize variables for the Fibonacci sequence
a <- 0
b <- 1

# Print the first two terms (0 and 1) of the sequence
cat("Fibonacci sequence:\n")
cat(a, b)
count <- 2 
repeat {
  next_term <- a + b
  

  if (next_term > 500) {
    break
  }
  

  cat(" ", next_term)
  a <- b
  b <- next_term
  

  count <- count + 1
  
  
    break
  }
```

## Using Basic Graphics (plot(),barplot(),pie(),hist())
### 4. Import the dataset as shown in Figure 1 you have created previously.

a. What is the R script for importing an excel or a csv file? Display the first 6 rows of
the dataset? Show your codes and its result
```{r}
library(readxl)
Shoes <- read_excel("Shoes.xlsx")
Shoes
```

b. Create a subset for gender(female and male). How many observations are there in
Male? How about in Female? Write the R scripts and its output.

```{r}
subsetMale <- subset(Shoes,Gender == "M")
subsetMale
subsetFemale <- subset(Shoes,Gender == "F")
subsetFemale
```
There are 14 observation in Male and 14 observation also in Female


### c. Create a graph for the number of males and females for Household Data. Use plot(), chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and its result.
```{r}
library(readr)
HouseholdData <- read_csv("HouseholdData.csv")

```

### 5. The monthly income of Dela Cruz family was spent on the following:
a. Create a piechart that will include labels in percentage.Add some colors and title of
the chart. Write the R scripts and show its output.

```{r}
data <- c(60, 10, 5, 25)
labels <- c("Food", "Electricity", "Savings", "Miscellaneous")

colors <- c("maroon", "pink", "skyblue", "purple")


pie(data, labels = labels, col = colors)

legend("bottomright", legend = labels, fill = colors, title = "Categories")

title("The monthly spent of Dela Cruz family")

```

### 6. Use the iris dataset.
```{r}
data(iris)
iris
```
a. Check for the structure of the dataset using the str() function. Describe what you
have seen in the output.
```{r}
str(iris)
```
The str function tells the structure of the iris data set, that there are 150 objects in 5 variables

b. Create an R object that will contain the mean of the sepal.length,
sepal.width,petal.length,and petal.width. What is the R script and its result?

```{r}
num6b<-mean(iris$Sepal.Length)
num6b
```

c. Create a pie chart for the Species distribution. Add title, legends, and colors. Write
the R script and its result.
```{r}
data(iris)

species <- table(iris$Species)

colors <- c("setosa" = "yellowgreen", "versicolor" = "green", "virginica" = "yellow")

pie(species, labels = species, col = colors)

legend("topright", legend = names(species_counts), fill = colors, title = "Species")

title("Species Distribution in Iris Dataset")

```

